Title

### 2023-11-16 main.tex
and so the crazy refactoring process sees the sunlight after some months in the dark!

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. 
% \revnote{So another way to see this is that the simulation through the
% proposed decomposition works only for depolarising channels, and fails
% otherwise. } 
% \tbnote{Contestar en la carta que funciona hasta cierto punto para todos los
% canales propuestos y que se cuantifica qué tan bien funciona o no usando la
% fidelidad}
This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
% Moreover, the algorithm of \fref{Fig2} is not optimal for
% unitary channels (that is, the channels corresponding to the vertices of the
% tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
% baja segun la imagen, por lo que podemos ver que los unitarios
% tienen una fid baja.} 
% \tbnote{
Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
channels in the edges of the tetrahedron, which corresponds to unitary channels. 
% }
 These simple channels could be accomplished more
efficiently by simply applying the corresponding Pauli operator directly. \revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
\tbnote{Este comentario se conecta con lo del 
primer comentario, que no sé bien cómo contestar.}
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
\tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
{\color{green} This disadvantage comes from the fact
that the circuit is applicable to any Pauli channel, which that means that sometimes
it is not the most straightforward algorithm to simulate a Pauli channel.
However, the main advantages are that the algorithm is simple, and if we want 
to simulate many Pauli channels (for example,
for simulating a Pauli dynamical map as we will see later),
we only have to change a couple of angles in the circuit to move between 
different Pauli channels and not completely reconstruct the circuit. 
And as we will see, sometimes only changing
one angle in the circuit will be enough.}\\
$\;$\\

\tbnote{Sección que agregué:}\\

{\color{green}
\subsection{Simulation of a two-qubit Pauli channel}
\label{2qbit}
For the case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} would have two main
qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, since the quantum computer ibmq-lima we used does not have that many qubits,
we will simulate a Pauli channel that does not apply all two-qubit Pauli matrices to the system.
For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has $4$ Pauli operations, 
only $2$ ancilla qubits will be necessary, and it can be implemented
using the circuit of \fref{2qbit}b.

\begin{figure} % {{{
\centering
\includegraphics{images/qbit-im.pdf}
\caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation for the 2-qubit dephasing channel of \eref{2qbit-c}. The state on the two ancilla qubits can be constructed just as it was done for \fref{Fig2}. }
\label{2qbit}
\end{figure} % }}}

Just as for the one-qubit Pauli channels, this 
channel was implemented on IBM's ibmq-lima  quantum computer and we obtained the Choi 
matrix by doing quantum process tomography on
the main qubits. Then, we calculated the diamond fidelity for different values of $p$ and
obtained the results shown in \fref{2qbit}a. 
As can be seen in the figure, the fidelity doesn't vary much as we change the value of $p$,
and it stays at a value of around $0.75$, 
and it is biggest around $p=0$, corresponding to the identity channel.
}

@@

\begin{definition}{\textbf{1-Parameter Rotation Circuit:}}
A 1-Parameter Rotation (1PR) circuit is a parametrized quantum
circuit that includes only one gate dependent on a parameter $p$.
Moreover, the parametrized gate is a one-qubit rotation about any axis,
whether controlled or not.
\end{definition}
\revnote{This definition is vague - given the vagueness of the term "quantum circuit".
 Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.}
 \tbnote{Agregar lo siguiente a la definición:}

{\color{green}
Therefore, a 1PR circuit implements a unitary operator $U(p)$ on some number $N$ of qubits,
such that $U$ depends on the parameter $p$ only locally on one specific qubit.
}

@@

\begin{theorem}
\label{theorem2}
Consider a 1PR circuit of $N$ qubits parametrized by $p$
and denote by $U(p)$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align}
U(p)|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
\label{eq:uj}
\end{align}
with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states 
and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
c^j|c^j \rangle = 1$. Here $|j\rangle$ represents an element of the N-qubit  computational basis.
\end{theorem}
\textbf{Proof:}  \revnote{again, this is not a conclusion from theorem 1. This is literally Definition 1. Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N. Then the matrix representation of the operators is a $2^n \times 2^n$ matrix which is applied to the state j.... The explanation in words in not sufficient.} \tbnote{Cambié la siguiente oración por el párrafo en verde}
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

{\color{green} As before, from the definition of a 1PR circuit, we know that $U(p)$ can be decomposed as $ARB$, where 
$A,B$ are unitary operators acting on the $N$-qubit system
and $R$ is a rotation applied to one qubit.
From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$
rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones.
To prove this theorem,
we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
then $R_{\sigma_3}(2s(p))$ and finally $A$, with
the goal of getting to \eref{eq:uj}. }

@@

Finally, after having applied the rotation, the circuit applies gate $A$, 
so that the result is given by:
\begin{eqnarray*}
U|j\rangle = AR_{\sigma_3}(2s(p)) B|j\rangle = e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
\end{eqnarray*}
where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
states that satisfy $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ because $A$ is unitary. $\blacksquare$  \\
 $\;$ \\

@@

The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.
For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
using an optical arrangement, and  it was indeed done 
by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate). \revnote{there is literally one parameter in one qubit, of course it depends on one parameter...
 how can this be a result?}
\tbnote{Aquí la verdad no entiendo del todo qué intenta decir.
El resultado es que en ese paper sólo hubo que variar un parámetro
para hacer el bit phase flip, que coincde con lo que nosotros 
probamos sobre qué canales se pueden hacer con una rotación parametrizada (pues bit phase flip es uno de esos). }

@@

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps  selected at random
that can be implemented with a 1PR circuit in \fref{Fig5}. \revnote{This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example), }
\tbnote{Los mapas que ya mencionamos más a profundidad (depolarizing, phase damping, etc.) son esos ejemplos creo yo.
Pues son ejemplos de mapas útiles o conocidos (por lo menos el depolarizing y los bit flip, phase flip, bit phase flip) y que
probamos que se pueden hacer con una rotación parametrizada.}

@@

\revnote{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit. I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so.. what is the applicability of the theorem for higher dimensions?}

\tbnote{Añadí el párrafo en verde hablando de eso.}

In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise.}.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities.

Then, when working with Pauli dynamical maps,
we searched for a way of minimizing the amount of 
parametric operations in the circuit 
by requiring that only one single-qubit rotation depends on the parameter. \revnote{This reasoning I miss, simplifying for achieving what goal? } 
\tbnote{Le di una reescritura a esa frase.}
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.
\tbnote{Given this condition, we considered the space of Pauli maps that are possible to parametrize with one parameter, and 
gave some explicit examples for a system of one qubit. 
As the number of qubits gets bigger, the degrees of freedom for choosing a Pauli dynamical map also gets bigger,
so we would expect that the space of maps that can be done with only 
one parameter
becomes a smaller part of the whole space of Pauli dynamical maps.
However, some paradigmatic maps as the dephasing one we studied for 2 qubits in section \ref{2qbit} will still be
possible to do with a 1PR circuit (for this case, this can be seen by
noticing that said dephasing channel in \eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo}, which we proved
to be possible to implement with a 1PR circuit).}

In conclusion, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the effect that the error of a quantum computer have
on these simulations, quantified by the fidelity. \revnote{There is no quantification of this, it´s not even the focus of the paper} \tbnote{ya cambié la oración}
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning~\cite{Benedetti}.

>>>>

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. 
% \revnote{So another way to see this is that the simulation through the
% proposed decomposition works only for depolarising channels, and fails
% otherwise. } 
% \tbnote{Contestar en la carta que funciona hasta cierto punto para todos los
% canales propuestos y que se cuantifica qué tan bien funciona o no usando la
% fidelidad}
This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
% Moreover, the algorithm of \fref{Fig2} is not optimal for
% unitary channels (that is, the channels corresponding to the vertices of the
% tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
% baja segun la imagen, por lo que podemos ver que los unitarios
% tienen una fid baja.} 
% \tbnote{
Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
channels in the edges of the tetrahedron, which corresponds to unitary channels. 
% }
These channels could be accomplished more
efficiently by simply applying the corresponding unitary operator directly. 
% \revnote{I wholeheartedly agree with this statement, and I would go so far as
% to claim that this is true in general, even at the center of the tethraedron.}
% \tbnote{Este comentario se conecta con lo del 
% primer comentario, que no sé bien cómo contestar.}
% Nevertheless, due to its general design to accommodate any Pauli channel, the
% algorithm employs numerous quantum gates even in such scenarios. 
In this case we would be trading generality for fidelity. 
% \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
% \tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
The main advantage of the algorithm is that we can simulate with a unitary 
circuit
% simple, and if we want 
% to 
any Pauli channel, 
% (for example,
% for simulating a Pauli dynamical map as we will see later),
only varying a couple of angles in the circuit.
%  to move between 
% different Pauli channels and not completely reconstruct the circuit. 
In fact, as we will see, sometimes only changing one angle in the circuit will
be enough to simulate many non-unitary dynamical maps of physical interest. 
\cpnote{Revisa estas ultimas frases. Reformule lo que pusiste.}

% {\color{green} This disadvantage comes from the fact
% that the circuit is applicable to any Pauli channel, which that means that sometimes
% it is not the most straightforward algorithm to simulate a Pauli channel.
% However, the main advantages are that the algorithm is simple, and if we want 
% to simulate many Pauli channels (for example,
% for simulating a Pauli dynamical map as we will see later),
% we only have to change a couple of angles in the circuit to move between 
% different Pauli channels and not completely reconstruct the circuit. 
% And as we will see, sometimes only changing
% one angle in the circuit will be enough.}\\
% $\;$\\
% 
% \tbnote{Sección que agregué:}\\
% }}}
\subsection{Simulation of a two-qubit Pauli channel} \label{2qbit} % {{{
% {\color{green}
For the general case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} requires two main
qubits and four ancilla qubits.
% , on which it would be necessary to create the state $\sum_{\vec{\gamma}}
% b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, the quantum computer which we are using has only \cpnote{cuantos qubits 
tiene esa compu?}.
does not have that many qubits,
We can still simulate a two qubit Pauli channel that does not apply all 
two-qubit Pauli matrices to the system\cpnote{that applies at most tantos operaciones 
de Pauli}.
For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has four Pauli operations, 
only $2$ ancilla qubits will be necessary, and thus it can be implemented
using the circuit of \fref{2qbit}b.

\begin{figure} % {{{
\centering
\includegraphics{images/qbit-im.pdf}
\caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation
for the 2-qubit dephasing channel of \eref{2qbit-c}. The state on the two
ancilla qubits can be constructed just as it was done for \fref{Fig2}.
\cpnote{Este caption no está copleto. Falta describir la a y luego la b. De hecho 
dado que primero proponemos el circuito y luego vemos la fidelidad, propngo 
poenr el circuito arriba y la fidelidad abajo. TAbien describir ambas cosas. } }
\label{2qbit}
\end{figure} % }}}

Just as for the one-qubit Pauli channels, this 
channel was implemented on IBM's ibmq-lima  quantum computer. We obtained the Choi 
matrix by doing quantum process tomography on
the main qubits. Then, we calculated the diamond fidelity for different values of $p$ and
obtained the results shown in \fref{2qbit}a. 
As can be seen in the figure, the fidelity doesn't vary much as we change the value of $p$.
It stays at a value of around $0.75$, and it is biggest around $p=0$,
corresponding to the identity channel\cpnote{Una descripcion mas precisa de
estos valores por favor.}
% }

@@

\begin{definition}{\textbf{1-Parameter Rotation Circuit:}}
A 1-Parameter Rotation (1PR) circuit is a parametrized quantum
circuit that includes only one gate dependent on a parameter $p$.
Moreover, the parametrized gate is a one-qubit rotation about any axis,
whether controlled or not.
\end{definition}
% \revnote{This definition is vague - given the vagueness of the term "quantum circuit".
%  Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.}
%  \tbnote{Agregar lo siguiente a la definición:} 
%  
Therefore, a 1PR circuit implements a unitary operator $U(p)$ on some number $N$ of qubits,
such that $U$ depends on the parameter $p$ only locally on one specific qubit.

@@

\begin{theorem}
\label{theorem2}
Consider a 1PR circuit of $N$ qubits parametrized by $p$
and denote by $U(p)$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align}
U(p)|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
\label{eq:uj}
\end{align}
with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states 
and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
c^j|c^j \rangle = 1$. Here $|j\rangle$ represents an element of the N-qubit  computational basis.
\end{theorem}
\textbf{Proof:}  
% \revnote{again, this is not a conclusion from theorem 1. This is literally
% Definition 1. Also, use the proper notation here - make A and B operators
% living on an dim N Hilbert state, and R explixitly dependent on s and operating
% on qubit N. Then the matrix representation of the operators is a $2^n \times
% 2^n$ matrix which is applied to the state j.... The explanation in words in not
% sufficient.} \tbnote{Cambié la siguiente oración por el párrafo en verde}
% We can conclude from theorem 1 that $U=ARB$,
% where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
% applied to the last qubit and controlled by some of the other ones. 
% {\color{green} 
As before, from the definition of a 1PR circuit, we know that $U(p)$ can be
decomposed as $ARB$, where $A,B$ are unitary operators acting on the $N$-qubit
system and $R$ is a rotation applied to one qubit.  From theorem 1, we conclude
that $R$ can be taken in general as a $\sigma_3$ rotation of angle $2s(p)$
applied to the last qubit and controlled by some of the other ones.  To prove
this theorem, we will apply $U(p)$ to $|j\rangle$ by first applying $B$, then
$R_{\sigma_3}(2s(p))$ and finally $A$, with the goal of getting to
\eref{eq:uj}. 
% }

@@

Finally, after having applied the rotation, the circuit applies gate $A$, 
so that the result is given by:
% \begin{eqnarray*}
\begin{align}
U|j\rangle &= AR_{\sigma_3}(2s(p)) B|j\rangle \nonumber \\
           &= e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle 
              + A |\tilde{c}^j\rangle \nonumber \\
           &= e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
\end{align}
% \end{eqnarray*}
where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
states that satisfy $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ because $A$ is unitary. $\blacksquare$  \\
 $\;$ \\

@@

The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.
For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
using an optical arrangement, and  it was indeed done 
by varying only one angle that depends on the parameter $p$ (the angle of a
half waveplate). 
% \revnote{there is literally one parameter in one qubit, of
% course it depends on one parameter...
%  how can this be a result?}
% \tbnote{Aquí la verdad no entiendo del todo qué intenta decir.
% El resultado es que en ese paper sólo hubo que variar un parámetro
% para hacer el bit phase flip, que coincde con lo que nosotros 
% probamos sobre qué canales se pueden hacer con una rotación parametrizada (pues bit phase flip es uno de esos). }

@@

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps  selected at random
that can be implemented with a 1PR circuit in \fref{Fig5}. 
% \revnote{This is
% interesting, instead of giving only some random examples, I would actually
% explore more in details the zoology of this class of dynamical maps - if lucky,
% you would find class of interesting problems that can be simulated effectively
% in an experimental setup by just accessing one parameter (as the authors say,
% just with one set of waveplates, for example), }
% \tbnote{Los mapas que ya mencionamos más a profundidad (depolarizing, phase damping, etc.) son esos ejemplos creo yo.
% Pues son ejemplos de mapas útiles o conocidos (por lo menos el depolarizing y los bit flip, phase flip, bit phase flip) y que
% probamos que se pueden hacer con una rotación parametrizada.}

@@

% \revnote{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit. I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so.. what is the applicability of the theorem for higher dimensions?}
% 
% \tbnote{Añadí el párrafo en verde hablando de eso.}
% 
In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps
by using parametrized quantum circuits.
%  \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise.}.
Furthermore, we implemented single-qubit Pauli channels
on one of IBM's quantum computers
and obtained their fidelities.

Then, when working with Pauli dynamical maps,
we searched for a way of minimizing the amount of 
parametric operations in the circuit 
by requiring that only one single-qubit rotation depends on the parameter. 
% \revnote{This reasoning I miss, simplifying for achieving what goal? } 
% \tbnote{Le di una reescritura a esa frase.}
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.
\tbnote{Given this condition, we considered the space of Pauli maps that are
possible to parametrize with one parameter, and gave some explicit examples for
a system of one qubit.  As the number of qubits gets bigger, the degrees of
freedom for choosing a Pauli dynamical map also gets bigger, so we would expect
that the space of maps that can be done with only one parameter
becomes a relatively smaller part of the whole space of Pauli dynamical maps.
However, some paradigmatic maps as the dephasing one we studied for 2 qubits in
section \ref{2qbit} will still be possible to do with a 1PR circuit (for this
case, this can be seen by noticing that said dephasing channel in
\eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo},
which we proved to be possible to implement with a 1PR circuit).}
\cpnote{Reescribe lo anterior sin hacer referencias a ecuaciones o secciones.}

In conclusion, this work presents yet another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the effect that the error of a quantum computer have
on these simulations, quantified by the fidelity. 
% \revnote{There is no quantification of this, it´s not even the focus of the paper} \tbnote{ya cambié la oración}
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning~\cite{Benedetti}.
